Community Detection in the Setting of Generalized Random Dot Product Graphs

### 2023-01-12 slides/slides.Rmd
starting to add references

```{r mbconnectome-kcurves, fig.height = 2, fig.width = 8, cache = TRUE, out.width = '100%'}
set.seed(123456)

@@

>>>>

```{r mbconnectome-kcurves, fig.height = 2, fig.width = 8, cache = TRUE, out.width = '100%', fig.cap = 'Left and right hemispheres of the Drosophila connectome (top), ASEs (middle), and fitted curves (bottom).'}
set.seed(123456)

@@

## Expected Degree and Sparsity Factor

Let $d_1, ..., d_n$ be the degrees of vertices $v_1, ..., v_n$. 
For $P$ defined by a block model or GRDPG, $E[d_i] = O(n)$. 
In most real networks, the degree does not scale linearly with the size of the network.

Introduce a sparsity factor $\rho_n$ such that $A \sim \BG(\rho_n P)$.

* Sparse regime: $\lim\limits_{n \to \infty} \rho_n \to 0$
* Dense regime: $\rho_n = 1$

Most results still require $n \rho_n = \omega (\log^c n)$, i.e., 
expected degree still diverges, but at a logarithmic rate.

## References
